On Secure Delegation of SampBQP with a Classical Client

### 2020-02-08 bqp.tex
Add Skype discussion notes

\begin{protocol}{1-message $\QPIP_1$ protocol $\PiMF = (\PMF, \VMF)$ for $\BQP$ language $L$}
	\label{proto:BQP}
	Common input: $x\in\set{0,1}^n$. 
	\begin{enumerate}
		\item The verifier generates $\Lambda \leftarrow \cVMF{1}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state.
		\item The prover generates a certificate state $\rho\leftarrow\cPMF{2}(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier applies the measurement $\Lambda$ to $\rho$ qubit-by-qubit.
			Let $w \in \set{0,1}^n$ denote the measurement outcome.
			It verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
	\end{enumerate}
\end{protocol}

@@

\cref{proto:BQP} has negligible completeness and soundness.
Now we compile it using $\mathsf{QHE}$ in order to also achieve blindness:

\begin{protocol}{Blind protocol $\Piblind = (\Pblind, \Vblind)$ for $\BQP$}
	\label{proto:BlindBQP}
	Let $x\in\set{0,1}^n$ be an input for $\Vblind$.
	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPMF{2}$.
	\begin{enumerate}
		\item The verifier generates $\Lambda\leftarrow\cVMF{1}(x)$.
			On input $\Lambda$, it computes $\Lambda'$ using \cref{decodeMeasureOrder}.
			Then it generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$ and $y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
			It sends $y$ and $evk$ to the prover.
		\item The prover homomorphically evaluates $\cPMF{2}$ on input $y$, generating $\sigma\leftarrow\mathsf{QHE.Eval}(\cPMF{2}, y)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $ct\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct)$,
			and then $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

@@

	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ violating the soundness guarantees of $\Piblind$,
	then we can use it to construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$.

@@

	We define $\PMFstar$ to first generate
	$$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}$$
	and
	$$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$$
	It then sends $y$ and $evk$ to $\Pblindstar$ and gets $\sigma$ back.
	Finally, it generates
	$$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$$
	and sends it to $\VMF$ qubit-by-qubit.

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.

	By assumption, $\Vblind$ has a non-negligible probability to accept after receiving $\sigma$.
	In other words, let $\Lambda\leftarrow\cVMF{1}$, and define $\Lambda'$ by \cref{decodeMeasureOrder},
	then with non-negligible probability
	$$\cVMF{3}(x, \Lambda, \widehat{\mathsf{QHE.Dec}_{sk}}(\Lambda'(\sigma))=acc$$
	which is equivalent to
	$$\cVMF{3}(x, \Lambda, \Lambda(\rho))=acc$$
	That is, $\PMFstar$ violates the soundness of $\PiMF$.
\end{prf}

@@

We give a high-level overview of the compiliation results.

\begin{protocol}{\Cref{proto:BlindBQP} compiled using Mahadev's measurement protocol \Ethan{Give this a name}}
	\label{proto:QPIP0BQP}
	\begin{enumerate}
		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, y$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
			On input $\Lambda'$, it generates $k, td$.
			It sends $k, evk, y$ to the prover.
		\item The prover, on inputs $k, evk, y$, generates classical ``commitment" $m$ and internal state $\ket{st}$.
			It sends $m$ to the verifier.
		\item The verifier sends the prover a public fair coin $c\in{0,1}$.
		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
		\item The verifier, on inputs $k, td, m, c, a, sk$, generates and outputs either $acc$ or $rej$.
	\end{enumerate}
\end{protocol}

>>>>

\begin{protocol}{1-message $\QPIP_1$ protocol $\PiMF = (\PMF, \VMF)$ for $\BQP$ language $L$}
	\label{proto:BQP}
	Common input: $x\in\set{0,1}^n$. 
	\begin{enumerate}
		\item The verifier generates $\Lambda \leftarrow \cVMF{1}(x)$, where $\Lambda=\Lambda_1\otimes\ldots\otimes\Lambda_m$; each $\Lambda_i$ is a single-qubit $X$ or $Z$ measurement and $m=\poly(n)$ is the length of the prover's certificate state. \Ethan{Switch steps 1 and 2}
		\item The prover generates a certificate state $\rho\leftarrow\cPMF{2}(x)$  and sends $\rho$ to the verifier qubit-by-qubit.
		\item The verifier applies the measurement $\Lambda$ to $\rho$ qubit-by-qubit.
			Let $w \in \set{0,1}^m$ denote the measurement outcome.
			It verifies the measurement outcome and produces a decision $o\leftarrow\cVMF{3}(x, \Lambda, w)$ where $o\in\set{acc, rej}$ and $\cVMF{3}$ is a classical polynomial-time algorithm.
	\end{enumerate}
\end{protocol}

@@

\Ethan{Give the theorem above a corresponding algorithm}

\Cref{proto:BQP} has negligible completeness and soundness.
Now we compile it using $\mathsf{QHE}$ in order to also achieve blindness:

\begin{protocol}{Blind $\QPIP_1$ 1-message protocol $\Piblind = (\Pblind, \Vblind)$ for $\BQP$ language $L$}
	\label{proto:BlindBQP}
	Verifier's input: $x\in\set{0,1}^n$.

	Let $d=\poly(n)$ be the depth of the circuit corresponding to $\cPMF{2}$.
	\begin{enumerate}
		\item The verifier generates $\Lambda\leftarrow\cVMF{1}(x)$.
			On input $\Lambda$, it computes $\Lambda'$ using \cref{decodeMeasureOrder}.
			Then it generates $(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$ and $y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$.
			It sends $y$ and $evk$ to the prover.
			\Ethan{Do two steps. Keygens first, lambda next. For keygen step, say more in words and describe $d$. Remember to specify $x$ when talking about $d$ and $\cPMF{2}$}
		\item The prover homomorphically evaluates $\cPMF{2}$ on input $y$, generating $\sigma\leftarrow\mathsf{QHE.Eval}(\cPMF{2}, y)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $ct\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct)$,
			and then $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

\Ethan{Change steps orders above. 1. verifier enc and send y 2. prover sends something back 3. verifier sample lambda}

@@

	Suppose for the sake of contradiction that there exists some cheating prover $\Pblindstar$ violating the soundness guarantees of $\Piblind$ 
	\Ethan{Define some $\epsilon$ here. Also ``non-negligible" = ``noticeable"},
	then we can use it to construct a prover $\PMFstar$ violating the soundness guarantees of $\PiMF$.

@@

	\Ethan{Add the ``simulate" thing back}

	We define $\PMFstar$ to first generate
	$(pk, sk, evk)\leftarrow\mathsf{QHE.Keygen}$
	and
	$y\leftarrow\mathsf{QHE.Enc}_{pk}(x)$
	It then sends $y$ and $evk$ to $\Pblindstar$ and gets $\sigma$ back.
	Finally, it decrypts
	$\rho\leftarrow\mathsf{QHE.Dec}_{sk}(\sigma)$
	and sends it to $\VMF$ qubit-by-qubit.

    \Ethan{Rewrite the following proof again; write in terms of interactions this time. See google docs. Same success probability. Compare interactions}

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
    By assumption, $\Vblind$ has a non-negligible probability to accept after receiving $\sigma$.
	In other words, let $\Lambda\leftarrow\cVMF{1}$, and define $\Lambda'$ by \cref{decodeMeasureOrder},
    \Ethan{Give theorem 3.2 an algorithm}
	then with non-negligible probability
	$$\cVMF{3}(x, \Lambda, \widehat{\mathsf{QHE.Dec}_{sk}}(\Lambda'(\sigma))=acc$$
	which is equivalent to
	$$\cVMF{3}(x, \Lambda, \Lambda(\rho))=acc$$
	That is, $\PMFstar$ violates the soundness of $\PiMF$.
\end{prf}

@@

We give a high-level overview of the compiliation results. \Ethan{Maybe just delete it and give name only}

\begin{protocol}{\Cref{proto:BlindBQP} compiled using Mahadev's measurement protocol \Ethan{Give this a name}}
	\label{proto:QPIP0BQP}
	\begin{enumerate}
		\item The verifier generates $\Lambda, \Lambda', pk, sk, evk, y$ the same way as in \cref{proto:BlindBQP}. \Ethan{Need more notation? But how?}
			Then, using $\Lambda'$, it generates $k, td$.
			It sends $k, evk, y$ to the prover.
		\item The prover, on inputs $k, evk, y$, generates classical ``commitment" $m$ and internal state $\ket{st}$.
			It sends $m$ to the verifier.
		\item The verifier sends the prover a public coin $c\in\set{0,1}$.
		\item The prover, on inputs $c$ and $\ket{st}$, generates classical $a$ and sends it to the verifier.
		\item The verifier, on inputs $k, td, m, c, a, sk$, generates and outputs either $acc$ or $rej$.
	\end{enumerate}
\end{protocol}

\Ethan{
    Need to say more about step 5.
    It's a compiler here.
    Need to say stuff about interface
    see protocol 5.1; protocol is the most important
    interface uses only lambda
    if hadamard round, get measurement outcome corresponding to sigma
    how to decode

    Describe in words what's 5.1
    Leave author note for theorem for now
}
